---
title: "Data Import"
output: github_document
---
```{r}
setwd("/Users/rachellemay/Desktop/data_wrangling_1")
```


## to insert this code chunk below, press "option, command, i"
```{r setup}
library(tidyverse)
```

## Read in some data

Read in the litters dataset.

```{r}
litters_df = read_csv("/Users/rachellemay/Desktop/data_wrangling_1/data/FAS_litters.csv")
litters_df = janitor :: clean_names(litters_df)
```

## first step of code chunk: this above is a relative path for importing data
## second step: clean up data import with clean_names function; in order to make command work use janitor :: function()

## Take a look at the data

Printing in the console. 

```{r}
litters_df

```
## head function"() gives first 6 rows of dataset

```{r}
head(litters_df)
```
## tail function () gives last 6 rows
```{r}
tail(litters_df)
```
## skim gives you a rundown- kind of handy but a little gimmicky

```{r}
skimr :: skim(litters_df)
```
## view function is better bc opens new window and allows you to interact w dataset
## avoid putting view in R markdown tho


# Options to read_csv
## "skip = 10" means skip 10 rows of dataset
```{r}
litters_df = read_csv("/Users/rachellemay/Desktop/data_wrangling_1/data/FAS_litters.csv", skip = 10, col_names = FALSE)
```
## you could also do read_csv(directory, na = c("", "NA", ".", "999") so that R knows those are missing values in dataset

check out '?read_csv()' for more info

## other file formats

Read in an excel file

```{r}
library(readxl)
mlb_df = read_excel("/Users/rachellemay/Desktop/data_wrangling_1/data/mlb11.xlsx", range = "A1:F7"")
mlb_df
```

Read in a SAS file. 

```{r}
library(haven)
pulse_df = read_sas("/Users/rachellemay/Desktop/data_wrangling_1/data/public_pulse_data.sas7bdat")
pulse_df
```

## comparison with Base R

what about 'read.csv'...?
## never use read.csv!!!

## it will give entire dataset, weird col names, harder to manage

## Exporting data

Export the mlb sub-table

```{r}
write_csv(mlb_df, "/Users/rachellemay/Desktop/data_wrangling_1/data/mlb_subtable.csv")
```


