---
title: "Data Import"
output: github_document
---

## to insert this code chunk below, press "option, command, i"
```{r setup}
library(tidyverse)
```

## Read in some data

Read in the litters dataset.

```{r}
litters_df = read_csv("/Users/rachellemay/Desktop/data_wrangling_1/data/FAS_litters.csv")
litters_df = janitor :: clean_names(litters_df)
```

## first step of code chunk: this above is a relative path for importing data
## second step: clean up data import with clean_names function; in order to make command work use janitor :: function()

## Take a look at the data

Printing in the console. 

```{r}
litters_df

```
## head function"() gives first 6 rows of dataset

```{r}
head(litters_df)
```
## tail function () gives last 6 rows
```{r}
tail(litters_df)
```
## skim gives you a rundown- kind of handy but a little gimmicky

```{r}
skimr :: skim(litters_df)
```
## view function is better bc opens new window and allows you to interact w dataset
## avoid putting view in R markdown tho


